The dictionary for characters of smooth group schemes

### 2016-05-21 followup.tex
Small fixes to intro

As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
virtual Weil perverse sheaves on group schemes over finite fields.

In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
In this case, it can be shown that there is a forgetful functor taking every object in $\CCS(G)$ to a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,
but they are precisely the part needed to describe characters of such groups.
\bigskip

>>>>

As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected, reductive groups over $p$-adic fields.
In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
virtual Weil perverse sheaves on group schemes over finite fields.

In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
In this case, it can be shown that there is a forgetful functor taking every object in $\CCS(G)$ to a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,
but they are precisely the part needed to describe one dimensional characters of such groups.
\bigskip
